---
title: "Week 06 HW"
author: "SZR"
format: gfm ## to save as a file that can be viewed in github
prefer-html: true
---

## Introduction
For this homework I am practicing working with *Quarto*.

This document shows:  
* a figure of body mass by flipper length by island  
* a table of average body mass and flipper length of only the Adelie species

## Libraries
```{r}
#| message: false
#| warning: false
  
library(tidyverse)
library(here)
library(palmerpenguins)
library(kableExtra)
library(dplyr)
```

# Plotting

Plotting **body mass** by **flipper length** according to **species** and faceted by **island**
```{r}
#| warning: false
#| fig-align: "center"
#| label: fig-penguin-sp-isl
#| fig-cap: "This figure shows body mass by flipper length for each species according to island"
penguins %>%
  ggplot(aes(x = body_mass_g, y = flipper_length_mm, color = species))+
  geom_point()+
  facet_grid(. ~ island)
```
@fig-penguin-sp-isl shows a positive relationship between **body mass** and **flipper length** among all 3 species and islands. Chinstrap and Adelie appear to be a similar size overall with Gentoo being much larger. 

```{r}
#| warning: false
#| message: false
#| label: tbl-penguin-adelie
#| tbl-cap: "Adelie by Island table"
#| 
filtered_penguins <- filter(penguins, species == "Adelie")
         
filtered_penguins %>%
  group_by(island) %>%
  summarise(mean_mass = mean(body_mass_g, na.rm = TRUE),
            mean_flipper = mean(flipper_length_mm, na.rm = TRUE)) %>%
  kbl()  %>% ## this is a kable table
  kable_classic() %>% ## to make a kable theme
  kable_styling(full_width = FALSE)
```
@tbl-penguin-adelie comparing the **mean mass** and **mean flipper length** of only the **Adelie penguins** sorted by island.

